High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-09 notebooks/mnist.qmd
done

λ = [0.1,0.215,0.215]

@@

combos = [
    (9,7),
    (6,0),
    (4,1),
    (2,3),
    (5,8),
]

n_each = 2
combos = reduce(vcat, [fill(c, n_each) for c in combos])

@@

```{julia}
final_plts = []
for (i, (factual, target)) in enumerate(combos)
    p1 = plts_eccco[i]
    p2 = plts_wachter[i]
    plt = Plots.plot(
        p1, p2, layout=(2,1), plot_title="Factual: $factual, Target: $target",
        size = (1200, 400),
    )
    display(plt)
    savefig(plt, joinpath("dev/rebuttal/www", "mnist_$(factual)to$(target)_$(i).png"))
    push!(final_plts, plt)
end
```

>>>>

```{julia}
Random.seed!(123)

λ = [0.1,0.22,0.22]

@@

combos = [
    (9,7),
    (7,2),
    (6,0),
    (4,1),
    (2,3),
    (5,8),
    (6,5),
    (1,7),
    (1,4),
    (0,3)
]

n_each = 3
combos = reduce(vcat, [fill(c, n_each) for c in combos])

@@

```{julia}
final_plts = []
for (i, (factual, target)) in enumerate(combos)
    p1 = plts_eccco[i]
    p2 = plts_wachter[i]
    plt = Plots.plot(
        p1, p2, layout=(2,1),
        size = (1200, 400),
    )
    display(plt)
    savefig(plt, joinpath("dev/rebuttal/www", "mnist_$(factual)to$(target)_$(i).png"))
    push!(final_plts, plt)
end
```
